---
title: "3ª Lista de Exercícios"
author: 
  - Eniedson Fabiano Pereira da Silva Junior - 119110512  
  - João Paulo Alves Dantas - 119210258  
  - Rodrigo Farias Oliveira - 118110711
output: html_document
---

```{css, echo=FALSE}
h1 {
  text-align: center;
  margin-bottom: 3rem;
}

img {
  text-align: center;
}
```

# Respostas

1. 
    a) `r pnorm(1.64)`

    b) `r dnorm(1.64)`

    c) `r pnorm(1.64)`

    d) `r pnorm(-1.64)`

    e) `r pnorm(1.64) - pnorm(-1.64)`

    f) `r 1 - pnorm(1.64)`

    g) `r qnorm(0.05)`

    h) `r qnorm(1 - 0.05)`
    
    i) 
``` {r}
a <- pnorm(1.64)
a

b <- dnorm(1.64)
b

c <- pnorm(1.64)
c

d <- pnorm(-1.64)
d

e <- pnorm(1.64) - pnorm(-1.64)
e

f <- 1 - pnorm(1.64)
f

g <- qnorm(0.05)
g

h <- qnorm(1 - 0.05)
h 
```

2.  
    a) `r 1 - pnorm(108, mean = 100, sd = 25)`

    b) `r dnorm(100, mean = 100, sd = 25)`

    c) `r pnorm(107, mean = 100, sd = 25) - pnorm(89, mean = 100, sd = 25)`

    d) `r pnorm(116, mean = 100, sd = 25) - pnorm(112, mean = 100, sd = 25)`

    e) `r pnorm(116, mean = 100, sd = 25) - pnorm(112, mean = 100, sd = 25)`

    f) `r pnorm(100, mean = 100, sd = 25) + pnorm(106, mean = 100, sd = 25, lower.tail = TRUE)`

    g) `r qnorm(0.05, mean = 100, sd = 25)`

    h) `r qnorm(1 - 0.05, mean = 100, sd = 25)`
    
    i) `r qnorm(1 - 0.975, mean = 100, sd = 25)`
    
    j)
``` {r}
a <- 1 - pnorm(108, mean = 100, sd = 25)
a

b <- dnorm(100, mean = 100, sd = 25)
b

c <- pnorm(107, mean = 100, sd = 25) - pnorm(89, mean = 100, sd = 25)
c

d <- pnorm(116, mean = 100, sd = 25) - pnorm(112, mean = 100, sd = 25)
d

e <- pnorm(116, mean = 100, sd = 25) - pnorm(112, mean = 100, sd = 25)
e

f <- pnorm(100, mean = 100, sd = 25) + pnorm(106, mean = 100, sd = 25, lower.tail = TRUE)
f

g <- qnorm(0.05, mean = 100, sd = 25)
g

h <- qnorm(1 - 0.05, mean = 100, sd = 25)
h

i <- qnorm(1 - 0.975, mean = 100, sd = 25)
i
```

3.
    a) `r pnorm(1, 2.9, 1.4)`

    b) `r pnorm(4, 2.9, 1.4, lower.tail = FALSE)`

    c) `r pnorm(2, 2.9, 1.4, lower.tail = FALSE)`

    d) `r pnorm(4, 2.9, 1.4) - pnorm(2.5, 2.9, 1.4)`

    e) `r qnorm(0.005, 2.9, 1.4)`

    f) `r 10000 * 0.005`

    g) `r qnorm(0.05, 2.9, 1.4)`

4.

5.
      