---
title: "3ª Lista de Exercícios"
author:
- Eniedson Fabiano Pereira da Silva Junior - 119110512
- João Paulo Alves Dantas - 119210258
- Rodrigo Farias Oliveira - 118110711
output:
  pdf_document: default
  html_document: default
---

```{css, echo=FALSE}
h1 {
  text-align: center;
  margin-bottom: 3rem;
}

img {
  text-align: center;
}
```

# Respostas

1. 
    a) `r pnorm(1.64)`

    b) `r pnorm(1.64) - pnorm(1.64)`

    c) `r pnorm(1.64)`

    d) `r pnorm(-1.64)`

    e) `r pnorm(1.64) - pnorm(-1.64)`

    f) `r 1 - pnorm(1.64)`

    g) `r qnorm(0.05)`

    h) `r qnorm(1 - 0.05)`
    
    i) 
``` {r}
a <- pnorm(1.64)
a

b <- pnorm(1.64) - pnorm(1.64)
b

c <- pnorm(1.64)
c

d <- pnorm(-1.64)
d

e <- pnorm(1.64) - pnorm(-1.64)
e

f <- 1 - pnorm(1.64)
f

g <- qnorm(0.05)
g

h <- qnorm(1 - 0.05)
h 
```

2.  
    a) `r 1 - pnorm(108, mean = 100, sd = 25)`

    b) `r pnorm(100, mean = 100, sd = 25) - pnorm(100, mean = 100, sd = 25)`

    c) `r pnorm(107, mean = 100, sd = 25) - pnorm(89, mean = 100, sd = 25)`

    d) `r pnorm(116, mean = 100, sd = 25) - pnorm(112, mean = 100, sd = 25)`

    e) `r pnorm(116, mean = 100, sd = 25) - pnorm(112, mean = 100, sd = 25)`

    f) `r pnorm(100, mean = 100, sd = 25) + pnorm(106, mean = 100, sd = 25, lower.tail = TRUE)`

    g) `r qnorm(0.05, mean = 100, sd = 25)`

    h) `r qnorm(1 - 0.05, mean = 100, sd = 25)`
    
    i) `r qnorm(1 - 0.975, mean = 100, sd = 25)`
    
    j)
``` {r}
a <- 1 - pnorm(108, mean = 100, sd = 25)
a

b <- pnorm(100, mean = 100, sd = 25) - pnorm(100, mean = 100, sd = 25)
b

c <- pnorm(107, mean = 100, sd = 25) - pnorm(89, mean = 100, sd = 25)
c

d <- pnorm(116, mean = 100, sd = 25) - pnorm(112, mean = 100, sd = 25)
d

e <- pnorm(116, mean = 100, sd = 25) - pnorm(112, mean = 100, sd = 25)
e

f <- pnorm(100, mean = 100, sd = 25) + pnorm(106, mean = 100, sd = 25, lower.tail = TRUE)
f

g <- qnorm(0.05, mean = 100, sd = 25)
g

h <- qnorm(1 - 0.05, mean = 100, sd = 25)
h

i <- qnorm(1 - 0.975, mean = 100, sd = 25)
i
```

3.
    a) `r pnorm(1, 2.9, 1.4)`

    b) `r pnorm(4, 2.9, 1.4, lower.tail = FALSE)`

    c) `r pnorm(2, 2.9, 1.4, lower.tail = FALSE)`

    d) `r pnorm(4, 2.9, 1.4) - pnorm(2.5, 2.9, 1.4)`

    e) `r qnorm(0.005, 2.9, 1.4)`

    f) `r 10000 * 0.005`

    g) `r qnorm(0.05, 2.9, 1.4)`

4. 
    a)
```{r, echo=FALSE}

x1 <- seq(-4, 4, length=100)

y1 <- dnorm(x1)

plot(x1,y1, type = "l", lwd = 2, axes = FALSE, xlab = "", ylab = "", )

x2 <- seq(-1.64, 1.64, length=100)

y2 <- dnorm(x2)

polygon(c(x2[1:100], x2[100], x2[1]), 
        c(y2[1:100], 0, 0),
        col = "#E0F2F1")

axis(1, at = seq(-4, 4, length=17), labels = c("-4", "-3,5", "-3", "-2,5", "-2", "-1,5", "-1", "-0,5", "0", "0,5", "1", "1,5", "2", "2,5", "3", "3,5", "4"), gap.axis = 1/4)
box()
```

    b)
```{r, echo=FALSE}

x1 <- seq(-4, 4, length=100)

y1 <- dnorm(x1)

plot(x1,y1, type = "l", lwd = 2, axes = FALSE, xlab = "", ylab = "", )

x2 <- seq(-1.96, 1.96, length=100)

y2 <- dnorm(x2)

polygon(c(x2[1:100], x2[100], x2[1]), 
        c(y2[1:100], 0, 0),
        col = "#E0F2F1")

axis(1, at = seq(-4, 4, length=17), labels = c("-4", "-3,5", "-3", "-2,5", "-2", "-1,5", "-1", "-0,5", "0", "0,5", "1", "1,5", "2", "2,5", "3", "3,5", "4"), gap.axis = 1/4)
box()
```

    c)
```{r, echo=FALSE}

x1 <- seq(-4, 4, length=100)

y1 <- dnorm(x1)

plot(x1,y1, type = "l", lwd = 2, axes = FALSE, xlab = "", ylab = "", )

x2 <- seq(-2.57, 2.57, length=100)

y2 <- dnorm(x2)

polygon(c(x2[1:100], x2[100], x2[1]), 
        c(y2[1:100], 0, 0),
        col = "#E0F2F1")

axis(1, at = seq(-4, 4, length=17), labels = c("-4", "-3,5", "-3", "-2,5", "-2", "-1,5", "-1", "-0,5", "0", "0,5", "1", "1,5", "2", "2,5", "3", "3,5", "4"), gap.axis = 1/4)
box()
```

5.
    a) (`r qnorm(0.05)`, `r qnorm(0.95)`) | z = `r qnorm(0.95)`
    
    b) (`r qnorm(0.025)`, `r qnorm(0.975)`) | z = `r qnorm(0.975)`
    
    c) (`r qnorm(0.005)`, `r qnorm(0.995)`) | z = `r qnorm(0.995)`
      